Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-02-09 manuscript/climate_sensitivity_draft.Rmd
discussion

Our analysis has the limitation that canopy positions were recorded in 2018, as opposed to the years of the droughts. However, because trees would generally advance towards more dominant positions as they grow and as neighbors die, changing canopy positions would bias against the acceptance of our hypothesis. The implication is that dominant crown positions did have a marginally negative influence on $Rt$, which makes sense in light of the vertical environmental gradients described above and agrees with previous studies showing greater drought sensitivity in more exposed trees [@suarez_factors_2004; @scharnweber_confessions_2019]. It is safe to assume that currently suppressed trees have always been suppressed, and their relatively low $Rt$ (after correcting for height effects) is real, likely as a result of competition (*[Sohn et al. 2016](https://www.sciencedirect.com/science/article/pii/S0378112716304029)*). The observed height-sensitivity of $Rt$, together with the apparent lack of importance of soil water availability, agrees with the concept that physiological limitations to transpiration under drought shift from soil water availability to the plant-atmosphere interface as forests age [@bretfeld_plant_2018], such that tall, dominant trees are the most sensitive in mature forests. Additional research comparing drought responses of young and old forest stands, along with short and tall isolated trees, would be valuable for more clearly disentangling the roles of tree height and crown exposure.

>>>>

Our analysis has the limitation that canopy positions were recorded in 2018, as opposed to the years of the droughts. However, because trees would generally advance towards more dominant positions as they grow and as neighbors die, changing canopy positions would bias against the acceptance of our hypothesis. The implication is that dominant crown positions did have a marginally negative influence on $Rt$, which makes sense in light of the vertical environmental gradients described above and agrees with previous studies showing greater drought sensitivity in more exposed trees [@suarez_factors_2004; @scharnweber_confessions_2019]. It is safe to assume that currently suppressed trees have always been suppressed, and their relatively low $Rt$ (after accounting for height effects) is real, perhaps as a result of competition (*[Sohn et al. 2016](https://www.sciencedirect.com/science/article/pii/S0378112716304029)*). The observed height-sensitivity of $Rt$, together with the apparent lack of importance of soil water availability, agrees with the concept that physiological limitations to transpiration under drought shift from soil water availability to the plant-atmosphere interface as forests age [@bretfeld_plant_2018], such that tall, dominant trees are the most sensitive in mature forests. Additional research comparing drought responses of young and old forest stands, along with short and tall isolated trees, would be valuable for more clearly disentangling the roles of tree height and crown exposure.
